Entrainment of low Mach number thermals in stratified domains

### 2019-06-05 tex/stratified_thermals.tex
Changes to abstract and intro.

\begin{abstract}
Large-scale convective flows called giant cells were once thought to transport the Sun's luminosity in the solar convection zone, but recent observations have called their existence into question.
In place of large-scale flows, some authors have suggested the solar luminosity may instead be transported by small droplets of rapidly falling, low entropy fluid.
This ``entropy rain'' could propagate as dense vortex rings, analogous to rising buoyant thermals in the Earth's atmosphere.
In this work, we develop an analytical theory describing the evolution of dense, negatively buoyant thermals.
We verify the theory with 2D and 3D simulations of laminar, axisymmetric thermals in highly stratified atmospheres.
Our results suggest that entropy rain driven at the surface of the Sun could fall into two categories: a \emph{stalling} regime in which the droplets slow down and expand, and a \emph{falling} regime in which the droplets accelerate and shrink as they propagate downwards.
We estimate that solar downflows should be in the falling regime and should remain large enough to shield their entropic signature from diffusive effects until they reach the base of the solar convective zone.
\end{abstract}

@@

Rather than appealing to giant cells, \cite{spruit1997} hypothesized that convective motions in the Sun may be primarily driven by cooling in narrow downflow lanes at the solar surface.
\citet{brandenburg2016} incorporated this ``entropy rain'' concept into a non-local mixing length theory, and suggested the entropy rain could take the form of propagating vortex rings. 
However, the vortex rings described by \citet{brandenburg2016} do not include a fundamental aspect of entropy rain: it has lower entropy than the background atmosphere.
Entropy rain is dense, and buoyancy forces will modify its dynamics.

It is important to understand how the filling fraction of these basic convective elements is affected by their negative buoyancy. 
In the context of Earth's atmosphere, ``thermals,'' or buoyant fluid regions which evolve into rising vortex rings, are thought to be the basic unit of convection \citep[e.g.,][]{romps2015}. 
Atmospheric thermals are buoyant and rise, but the term is also used for dense, falling fluid.
We thus study the entropy rain hypothesis by investigating the evolution of individual dense thermals.

Thermals in the Boussinesq limit have been well studied in the laboratory for decades \citep[see e.g.][]{morton&all1956, scorer1957}, and more recently through Direct Numerical Simulation \citep[DNS,][]{lecoanet&jeevanjee2018}. 
These studies find that thermals expand radially and decelerate as they propagate.
Such an expansion may prevent entropy rain from reaching the bottom of the solar convection zone.
However, this work does not include the effects of density stratification.

@@

$\,$\newline$\,$
\begin{acknowledgements}
This work was supported by NASA Headquarters under the NASA Earth and Space Science Fellowship Program -- Grant 80NSSC18K1199.
This work was additionally supported by  NASA LWS grant number NNX16AC92G.  
Computations were conducted with support by the NASA High End Computing (HEC) Program through the NASA  Advanced Supercomputing (NAS) Division at Ames Research Center on Pleiades with allocation GID s1647.
\end{acknowledgements}

>>>>

\begin{abstract}
Large-scale convective flows called giant cells were once thought to transport the Sun's luminosity in the solar convection zone, but recent observations have called their existence into question.
In place of large-scale flows, some authors have suggested the solar luminosity may instead be transported by small droplets of rapidly falling, low entropy fluid.
This ``entropy rain'' could propagate as dense vortex rings, analogous to rising buoyant thermals in the Earth's atmosphere.
In this work, we develop an analytical theory describing the evolution of dense, negatively buoyant thermals.
We verify the theory with 2D and 3D simulations of laminar, axisymmetric thermals in highly stratified atmospheres.
Our results show that dense thermals fall in two categories: a \emph{stalling} regime in which the droplets slow down and expand, and a \emph{falling} regime in which the droplets accelerate and shrink as they propagate downwards.
We estimate that solar downflows are in the falling regime and maintain their entropy perturbation against diffusion until they reach the base of the convection zone.
This suggests that entropy rain may be an effective nonlocal mechanism for transporting the solar luminosity.
\end{abstract}

@@

Rather than appealing to giant cells, \cite{spruit1997} hypothesized that convective motions in the Sun may be primarily driven by cooling in narrow downflow lanes at the solar surface.
\citet{brandenburg2016} incorporated this ``entropy rain'' concept into a non-local mixing length theory, and suggested the entropy rain could take the form of propagating vortex rings.
The entropy rain hypothesis assumes these small vortex rings can maintain their entropy perturbation as they traverse the entire solar convection zone.
This allows them to transport the solar luminosity via enthalpy fluxes.
However, the vortex rings described by \citet{brandenburg2016} do not include a fundamental aspect of entropy rain: entropy perturbations relative to the background atmosphere.
Entropy rain is dense, and buoyancy forces will modify its dynamics.

It is important to understand how the propagation of these basic convective elements is affected by their negative buoyancy. 
In the context of Earth's atmosphere, ``thermals,'' or buoyant fluid regions which evolve into rising vortex rings, are thought to be the basic unit of convection \citep[e.g.,][]{romps2015}. 
Atmospheric thermals are buoyant and rise, but the term is also used for dense, falling fluid.
We thus study the entropy rain hypothesis by investigating the evolution of individual dense thermals.

Thermals in the Boussinesq limit have been well studied in the laboratory for decades \citep[see e.g.][]{morton&all1956, scorer1957}, and more recently through Direct Numerical Simulation \citep[DNS,][]{lecoanet&jeevanjee2018}. 
These studies find that thermals expand radially and decelerate as they propagate.
Such a deceleration may cause the thermals to move so slowly they would diffuse away their entropy perturbation before reaching the bottom of the solar convection zone.
However, this work does not include the effects of density stratification.

@@

$\,$\newline$\,$
\begin{acknowledgements}
We'd like to thank Brett McKim and Nadir Jeevanjee for discussions about thermals and the laminar entrainment picture.
This work was supported by NASA Headquarters under the NASA Earth and Space Science Fellowship Program -- Grant 80NSSC18K1199.
This work was additionally supported by  NASA LWS grant number NNX16AC92G.  
DL is supported by Princeton Center for Theoretical Science and Lyman Spitzer Jr.~postdoctoral fellowships.
Computations were conducted with support by the NASA High End Computing (HEC) Program through the NASA  Advanced Supercomputing (NAS) Division at Ames Research Center on Pleiades with allocation GID s1647.
\end{acknowledgements}
